{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-10 thesis/thesis.tex
thick changebars
ack joan karen deb and catherine; tighten up surrounding prose to trim requisite two lines

%\newcommand\revision[1]{#1\xspace}
\newcommand\revision[1]{\cbstart{}#1\cbend\xspace}
%\newcommand\revisionminor[1]{#1\xspace}
\newcommand\revisionminor[1]{\cbstart{}#1\cbend\xspace}

@@

\begin{acknowledgments}
\revision{I honor here the many people who supported me during these 7 years and made this journey possible.

@@

{Many others have collaborated with me directly on the research itself,
whom I thank here in approximate chapter order.
Michael J. Sullivan and Nathaniel Wesley Filardo were Landslide's first users besides myself back in its prototype days.
Joshua Wise, Miriam Zimmerman, and Glenn Willen helped revise my explanation of DPOR in \Cref{chap:landslide}.
Professor Brandon Lucia provided valuable comments and revisions to \Cref{chap:quicksand}'s content
that ultimately led to its publication at OOPSLA 2016.
Michael J. Sullivan double-checked the proofs therein.
Professor Timothy Zhu from Penn State University
and Professor Haryadi Gunawi and TA Kevin Zhao from the University of Chicago
graciously allowed me to use their students as guinea pigs
and helped greatly to improve Landslide's stability and robustness for use beyond CMU's walls,
greatly enriching \Cref{chap:education}'s evaluation.
David Blum and Skye Toor provided
invaluable advice on statistical analysis
that helped me evaluate the student
% justify last line bc of manual page break
\unskip\parfillskip 0pt \par}

@@

\noindent
grade distributions therein.
Mario Dehesa-Azuara generously contributed the
transactional memory data structures
that make up about half of \Cref{chap:tm}'s evaluation suite.
%
Carlo Angiuli, Evan Cavallo, Ziv Scully, Jim McCann,
Matthew Maurer, Stefan Muller, Guillaume Didier,
Sol Boucher, and Michael J. Sullivan
helped me rehearse and polish the snake fight talk.

@@

I thank the Parallel Data Lab, my research group at CMU,
for supporting me at the PDL retreat every fall,
pushing me to refine my presentation skills and to network with strangers (now familiar faces) from industry.
%I also thank those %industry
I also thank the industry attendees
%from each of the PDL Consortium member companies
for their interest %, even in more theoretical work,
%and for the enlightening conversations resulting therefrom.
and enlightening conversations.
%Thanks to the anonymous OOPSLA reviewer who went the extra mile to read my supplementary proofs
%and urged me to improve the formalism to be more foundational
%(the lack of any stronger criticism a silent vote of confidence for their overall correctness).
Thanks to Nicholas D. Matsakis for the mentorship and collaboration during my two summers as a Rust research intern at Mozilla,
and to the rest of the Rust community as well for their %extremely important
work
bringing better concurrent programs to the world from a different angle.
I thank everyone outside my %immediate
research circle who
%whether at the retreat or otherwise,
insisted how cool my research was for directly helping students --
every such reminder helped me keep my head up during darker times.

>>>>

%\newcommand\revision[1]{#1\xspace}
\newcommand\revision[1]{\cbstart[0.5em]{}#1\cbend\xspace}
%\newcommand\revisionminor[1]{#1\xspace}
\newcommand\revisionminor[1]{\cbstart{}#1\cbend\xspace}

@@

\begin{acknowledgments}
\revision{I honor here the many who %made this journey of 7 long years possible.
supported me during these 7 long years and made this journey possible.

@@

{Many have collaborated with me directly on the research itself,
whom I thank here in approximate chapter order.
Michael J. Sullivan and Nathaniel Wesley Filardo were Landslide's first other users
%besides myself
back in its prototype days.
Joshua Wise, Miriam Zimmerman, and Glenn Willen helped revise my explanation of DPOR in \Cref{chap:landslide}.
Professor Brandon Lucia provided valuable revisions to \Cref{chap:quicksand}'s content
that ultimately led to its publication at OOPSLA 2016.
Michael J. Sullivan double-checked the proofs therein.
Professor Timothy Zhu from Penn State University
and Professor Haryadi Gunawi and TA Kevin Zhao from the University of Chicago
graciously allowed me to use their students as guinea pigs
and helped to improve Landslide's
%stability and
robustness for use beyond CMU's walls,
greatly enriching \Cref{chap:education}'s evaluation.
David Blum and Skye Toor provided
invaluable advice towards the statistical analysis
used therein.
%that helped me evaluate the student
%grade distributions therein.
Mario Dehesa-Azuara generously contributed the transactional
% justify last line bc of manual page break
\unskip\parfillskip 0pt \par}

@@

\noindent
memory data structures
that make up about half of \Cref{chap:tm}'s evaluation suite.
%
Carlo Angiuli, Evan Cavallo, Ziv Scully, Jim McCann,
Matthew Maurer, Stefan Muller, Guillaume Didier,
Sol Boucher, and Michael J. Sullivan
helped me rehearse and polish the snake fight talk.

@@

I thank the Parallel Data Lab, my research group at CMU,
for supporting me at the PDL retreat every fall,
pushing me to refine my presentation skills and to network with strangers (now familiar faces) from industry.
%I also thank those %industry
I also thank the industry attendees
%from each of the PDL Consortium member companies
for their interest %, even in more theoretical work,
%and for the enlightening conversations resulting therefrom.
and enlightening conversations.
Joan Digney and Karen Lindenfelser
make a lot of gears turn behind the scenes at PDL,
and Deb Cavlovich and Catherine Copetas
do likewise for CSD as a whole.
%Thanks to the anonymous OOPSLA reviewer who went the extra mile to read my supplementary proofs
%and urged me to improve the formalism to be more foundational
%(the lack of any stronger criticism a silent vote of confidence for their overall correctness).
Thanks to Nicholas D. Matsakis for the mentorship %and collaboration
during my two summers as a Rust research intern at Mozilla,
and to the rest of the Rust community as well for their %extremely important
work
bringing better concurrent programs into the world. %from a different angle.
And to everyone at large who
%outside my %immediate
%research circle who
%whether at the retreat or otherwise,
insisted how cool it was that my research helps students:
thank you for helping me keep my head up during darker times.
